\paperTitle

### 2014-04-29 doc/icml2014/directed.tex
Started working on asymptotic efficiency picture

\begin{algorithm}
  \caption{\LearnClique~(pseudoinverse)}
  \label{algo:learnclique}
  \begin{algorithmic}
    \REQUIRE Hidden clique $\sC$ with exclusive views (\propertyref{exclusive-views}).
    \ENSURE Marginal distribution of the clique $Z_\sC$.
      \STATE Identify exclusive views $\Sx{\sV} = \{x_{v_1}, \cdots, x_{v_m}\}$.
      \STATE Return $\mH_\sC \gets \mO_{\Sx{\sV}}( \mOpp{v_1}{i_i}\pinv, \cdots, {\mOpp{v_m}{i_m}}\pinv )$.
  \end{algorithmic}
\end{algorithm}
Of course, for $Z_{\sC}$ to be identifiable, we need various rank conditions,
which will be established in \sectionref{sampleComplexity}.

@@

From \citet{anandkumar13tensor} given \assumptionref{full-rank-plus},
we have that $\mOpphat{v}{i}$ converges to $\mOpp{v}{i}$ at a rate of $n^{-\frac12}$ with a constant that
depends polynomially on the $k$-th singular value of $\mOpp{v}{i}$.
%Of course, the singular value of $\mOpp{v}{i}$ become exponentially worse as $x_v$ and $h_i$ become farther.
%So while we can obtain consistent estimates, the sample complexity
%is exponential in the mimimum distance from $h_i$ to any three views, as to be expected.
%(\todo{say something
%quantitative?  annoying part is that we would have to bring in the bounds, so leave it out probably}).
% DONE: need to setup the asymptotic - it's not fresh in everyone's mind.
% Easy case
Next, we need to show that the hidden marginals $\hat Z_\sC$ converge to $Z_\sC$.
First, $\hat M_\sV$ is just an empirical average of multinomials over the data points.
Abusing notation slightly, we let $M_\sV$ also denote its $d^{m}$-dimensional vectorized version.
We also represent $\mH_\sC$ as
  a vector in $\Re^{k^m}$, and represent $\mOppAll \eqdef
  \mOpp{v_1}{i_1} \otimes \cdots \otimes
  \mOpp{v_m}{i_m}$ as a matrix in $\Re^{d^m \times
  k^m}$.
By the central limit theorem, we have:
$\sqrt{n} (\hat M_\sV - M_\sV) \convind \sN(0, \Sigma_\sV)$,
where $\Sigma_\sV$ is the \emph{asymptotic variance} of $\hat M_\sV$: 
% ARUN: I don't think so - \todo{doesn't this need to be multiplied by something?}
\begin{align*}
\Sigma_\sV \eqdef \dM_\sV - M_\sV M_\sV^\top, \quad \dM_\sV \eqdef \text{diag}(M_\sV).
\end{align*}

% PL: this is not obviously correct
%To address the first, we will need that the following assumption on the
%  parameters of the model:
%\begin{assumption} 
%  \label{asm:full-rank-plus}
%  For every clique $\sC = \{h_{i_1}, \cdots, h_{i_m}\} \in \sG$, let
%    $Z_\sC$ be the marginal distribution for that clique. 
%  Then every mode-$i$ unfolding of $Z_\sC$ has full column rank.\verify
%\end{assumption}
%Intuitively, the assumption guarantees that the marginal probability of
%  any hidden state is non-zero.

We can now use the delta-method to convert the above result into 
the asymptotic variance for the pseudoinverse version of $\LearnClique$:
\begin{lemma}[Asymptotic variance of pseudoinverse estimator for $Z_\sC$]
  \label{lem:mom-variance}  
  Assume $\hat M_{\sV}$ has asymptotic variance $\Sigma_\sV$ defined above.
  Then the asymptotic variance of $\hat Z_\sC$ is:
  \begin{align*}
    \Sigma^{\mom} &= \mOppAlli \Sigma_\sV \mOppAllit.
  \end{align*}
  %where ${\mOppAll}\pinv \eqdef {\mOpp{v_1}{i_1}}\pinv \otimes
  %\cdots \otimes {\mOpp{v_m}{i_m}}\pinv$, a $d^m \times k^m$ matrix.
\end{lemma}
\begin{proof}
For clique $\sC$, recall we have
  $Z_{\sC} = \mO_\sV(\mOppi{v_1}{i_1},\cdots,\mOppi{v_m}{i_m})$.
%Choosing to represent $Z_\sC$ and $M_\sV$ as vectors and
%$\mOppi{v_1}{i_1} \otimes \cdots \otimes \mOppi{v_m}{i_m}$ as the
%matrix,
We can rewrite this representation more compactly as: $Z_{\sC} = {\mOppAll}\pinv \mO_\sV$.
By the delta-method \cite{vaart98asymptotic},
% DONE: need to shorten
%we have that the asymptotic variance of $M_\sV$ is:
%\begin{align*}
%  \sqrt{n}(\hat M_\sV - M_\sV) \convind \sN(0, \Sigma_\sV),
%\end{align*}
%where $\Sigma_\sV$ is the variance of the observations. 
we immediately get:
$\sqrt{n}(\hat Z_\sC - Z_\sC) \convind \sN(0, \mOppAlli \Sigma_\sV \mOppAllit)$.
\end{proof}

>>>>

\begin{algorithm}
  \caption{\LearnClique~(pseudoinverse)}
  \label{algo:learnclique}
  \begin{algorithmic}
    \REQUIRE Hidden clique $\sC$ with exclusive views (\propertyref{exclusive-views}).
    \ENSURE Marginal distribution of the clique $Z_\sC$.
      \STATE Identify exclusive views $\Sx{\sV} = \{x_{v_1}, \cdots, x_{v_m}\}$.
      \STATE Return $\mH_\sC \gets \mO_{\sV}( \mOpp{v_1}{i_i}\pinv, \cdots, {\mOpp{v_m}{i_m}}\pinv )$.
  \end{algorithmic}
\end{algorithm}
Of course, for $Z_{\sC}$ to be identifiable, we need various rank conditions,
which will be established in \sectionref{sampleComplexity}.

@@

From \citet{anandkumar13tensor} given \assumptionref{full-rank-plus},
we have that $\mOpphat{v}{i}$ converges to $\mOpp{v}{i}$ at a rate of $n^{-\frac12}$ with a constant that
depends polynomially on the $k$-th singular value of $\mOpp{v}{i}$.

\todo{Present sample complexity bounds for $\mOpp{v}{i}$.}
\todo{Present sample complexity bounds for $Z_\sC$.}

% Easy case
% Next, we need to show that the hidden marginals $\hat Z_\sC$ converge to $Z_\sC$.
% First, $\hat M_\sV$ is just an empirical average of multinomials over the data points.
% Abusing notation slightly, we let $\hat M_\sV$ also denote its
% $d^{m}$-dimensional vectorized version.
% We also represent $\mH_\sC$ as
%   a vector in $\Re^{k^m}$, and represent $\mOppAll \eqdef
%   \mOpp{v_1}{i_1} \otimes \cdots \otimes
%   \mOpp{v_m}{i_m}$ as a matrix in $\Re^{d^m \times
%   k^m}$.
% By the central limit theorem, we have:
% $\sqrt{n} (\hat M_\sV - M_\sV) \convind \sN(0, \Sigma_\sV)$,
% where $\Sigma_\sV$ is the \emph{asymptotic variance} of $\hat M_\sV$: 
% % ARUN: I don't think so - \todo{doesn't this need to be multiplied by something?}
% \begin{align*}
% \Sigma_\sV \eqdef \dM_\sV - M_\sV M_\sV^\top, \quad \dM_\sV \eqdef \text{diag}(M_\sV).
% \end{align*}
% 
% Our next step will be to use the delta-method to convert the above
% result into the asymptotic variance for the pseudoinverse version of
% $\LearnClique$. 
% \begin{lemma}[Asymptotic variance of pseudoinverse estimator for $\tilde Z_\sC$]
%   \label{lem:mom-variance}  
%   Assume $\hat M_{\sV}$ has asymptotic variance $\Sigma_\sV$ defined above.
%   Then the asymptotic variance of $\hat{Z_\sC}$ is:
%   \begin{align*}
%     \Sigma^{\mom} &= \mOppAlli \Sigma_\sV \mOppAllit.
%   \end{align*}
%   %where ${\mOppAll}\pinv \eqdef {\mOpp{v_1}{i_1}}\pinv \otimes
%   %\cdots \otimes {\mOpp{v_m}{i_m}}\pinv$, a $d^m \times k^m$ matrix.
% \end{lemma}
% \begin{proof}
% For clique $\sC$, recall we have
%   $Z_{\sC} = \mO_\sV(\mOppi{v_1}{i_1},\cdots,\mOppi{v_m}{i_m})$.
% %Choosing to represent $Z_\sC$ and $M_\sV$ as vectors and
% %$\mOppi{v_1}{i_1} \otimes \cdots \otimes \mOppi{v_m}{i_m}$ as the
% %matrix,
% We can rewrite this representation more compactly as: $Z_{\sC} = {\mOppAll}\pinv \mO_\sV$.
% By the delta-method \cite{vaart98asymptotic},
% % DONE: need to shorten
% %we have that the asymptotic variance of $M_\sV$ is:
% %\begin{align*}
% %  \sqrt{n}(\hat M_\sV - M_\sV) \convind \sN(0, \Sigma_\sV),
% %\end{align*}
% %where $\Sigma_\sV$ is the variance of the observations. 
% we immediately get:
% $\sqrt{n}(\hat Z_\sC - Z_\sC) \convind \sN(0, \mOppAlli \Sigma_\sV \mOppAllit)$.
% \end{proof}
